Reduced order modeling of nonlinear problems using neural networks

### 2017-10-04 report/article.tex
Upload new version, sent to Jan on October 4th.

		\iffalse
		As their biological counterpart, \emph{artificial neural networks} (ANNs) \cite{Hay05} are computing systems consisting of information-processing units, called \emph{neurons}, interconnected through \emph{weighted synapses}. The attractive feature of ANNs lies in their capability of \emph{learning} from experience \cite{Kri07}. As a result, ANNs have found most used in those applications, such as cluster detection, image identification or speech recognition, which are difficult to address via computer algorithms using rule-based programming \cite{Mat16}. However, ANNs have been successfully applied also in more traditional contexts, e.g., continuous function approximation, as a valid alternative to the programming approach to investigate complexity, nonlinearity and uncertainties of a high order \cite{Nie15}.

		The learning of an ANN is accomplished through a \emph{training} process, during which the network is exposed to a collection of examples and its weights are properly adjusted so that it can provide reasonable responses in similar (yet not identical) situations. As shown later in the paper, the training and the subsequent evaluation of a neural network perfectly fit the offline-online framework, offering the POD-NN method a significant online speed-up with respect to the standard projection-based POD-Garlerkin (POD-G) RB procedure.
		\fi

@@

		Let $V_h \subset V$ be a suitable FE subspace of $V$ of (finite) dimension $N_h$, with $h \geq 0$ being the characteristic size of the underlying mesh $\Omega_h$ which discretizes the domain $\Omega$. The FE approximation of the weak problem \eqref{eq:pde-weak-reference} can be cast in the form: given $\bg{\mu} \in \mathcal{P}$, find $u_h(\bg{\mu}) \in V_h$ such that 
		\begin{equation}
			\label{eq:galerkin}
			g(u_h(\bg{\mu}), \, v_h; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v_h \in V_h \, .
		\end{equation}
		The discretization \eqref{eq:galerkin} is known as \emph{Galerkin approximation}, and therefore $u_h(\bg{\mu})$ is referred to as the \emph{Galerkin solution} to the problem \eqref{eq:pde-differential-reference}. Due to the nonlinearity of $g(\cdot, \, \cdot; \, \bg{\mu})$ in its first argument, one has to resort to some iterative method, e.g., Newton's method, to solve the Galerkin problem \eqref{eq:galerkin}. In this regard, let \[ dg[z](\cdot, \, \cdot; \, \bg{\mu}) ~ : ~ V \times V \rightarrow \mathbb{R} \]
		be the partial Frech\'et derivative of $g(\cdot, \, \cdot; \, \bg{\mu})$ with respect to its first argument, evaluated at $z \in V$. Starting from an initial guess $u_h^0(\bg{\mu})$, we construct a collection of approximations $\big\lbrace u_h^k(\bg{\mu}) \big\rbrace_{k \geq 0}$ to the Galerkin solution $u_h(\bg{\mu})$ by iteratively solving the linearized problems
		\begin{equation*}
			\label{eq:newton-linearized-problem}
			dg \big[ u_h^k(\bg{\mu}) \big](\delta u_h^k(\bg{\mu}), \, v_h; \, \bg{\mu}) = - g(u_h^k(\bg{\mu}), \, v_h; \, \bg{\mu}) \hspace*{0.3cm} \forall v_h \in V_h
		\end{equation*}
		in the unknown $\delta u_h^k(\bg{\mu}) \in V_h$, and then setting $u_h^{k+1}(\bg{\mu}) = u_h^k(\bg{\mu}) + \delta u_h^k(\bg{\mu})$.

@@

		As detailed in the previous section, the finite element discretization of the $\bg{\mu}$-dependent nonlinear differential problem \eqref{eq:pde-weak-reference}, combined with Newton's method, entails the assembly and resolution of (possibly) many linear systems of the form \eqref{eq:galerkin-linear-system}, whose dimension $N_h$ is directly related to $(i)$ the size of the underlying grid and $(ii)$ the order of the polynomial FE space adopted. Since the accuracy of the resulting discretization heavily relies on these two factors, a direct numerical approximation of the full-order model implies severe computational costs. Therefore, this approach is hardly affordable in \emph{many-query} and \emph{real-time} contexts, even resorting to high-performance parallel workstations. %where one is interested in a fast and reliable prediction of an \emph{output of interest}, i.e, a functional of the field variable $u(\bg{\mu})$, for many instances of $\bg{\mu} \in \mathcal{P}$ \cite{Dep08}. 
		This motivates the broad use of \emph{reduced-order} models across several inter-disciplinary areas, e.g., parameter estimation, optimal control, shape optimization and uncertainty quantification \cite{HSR16, QMN15}.

		Reduced basis methods seek an approximated solution to problem \eqref{eq:pde-weak-reference} as a linear combination of parameter-independent functions $\big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace \subset V_h$, called \emph{reduced basis functions}, built from a collection of high-fidelity snapshots $\big\lbrace u_h \left( \bg{\mu}^{(1)} \right), \, \ldots \, , u_h \left( \bg{\mu}^{(N)} \right) \big\rbrace$, where the discrete and finite set $\Xi_N = \big\lbrace \bg{\mu}^{(1)}, \, \ldots \, , \bg{\mu}^{(N)} \big\rbrace \subset \mathcal{P}$ may consist of either a uniform lattice or randomly generated points over the parameter domain $\mathcal{P}$ \cite{HSR16}. The basis functions \smash{$\big\lbrace \psi_l \big\rbrace_{1 \leq l \leq L}$} generally follow from a principal component analysis (PCA) of the set of snapshots (in that case, $N > L$), or they might coincide with the snapshots themselves (in that case, $N = L$). In the latter approach, typical of any \emph{greedy} method, the parameters \smash{$\big\lbrace \bg{\mu}^{(n)} \big\rbrace_{1 \leq n \leq N}$} must be carefully chosen according to some optimality criterium (see, e.g., \cite{Chen17}). Here, we pursue the first approach, employing the well-known proper orthogonal decomposition (POD) method \cite{Lia02, Vol08}, detailed in the following subsection.

		Assume now that a reduced basis is available and let $V_{\texttt{rb}} \subset V_h$ be the associated \emph{reduced basis space}, i.e.,
			V_{\texttt{rb}} = \text{span} \big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace \, .
		A \emph{reduced basis solution} $u_{L}(\bg{\mu})$ is sought in the form
			\label{eq:rb-solution}
			u_{L}(\bg{x}; \, \bg{\mu}) = \sum_{l = 1}^L u_{\texttt{rb}}^{(l)}(\bg{\mu}) ~ \psi_l(\bg{x}) ~ \in ~ V_{\texttt{rb}} \, ,
		with \[ \mathbf{u}_{\texttt{rb}}(\bg{\mu}) = \big[ u_{\texttt{rb}}^{(1)}(\bg{\mu}), \, \ldots \, , u_{\texttt{rb}}^{(L)}(\bg{\mu}) \big]^T \in \mathbb{R}^L \] be the \emph{reduced coefficients} (also called \emph{generalized coordinates}) for the expansion of the RB solution in the RB basis functions. To unearth $u_L(\bg{\mu})$, we proceed to project the variational problem \eqref{eq:pde-weak-reference} onto the RB space $V_{\texttt{rb}}$ by pursuing a standard Galerkin approach, leading to the following \emph{reduced basis problem}: given $\bg{\mu} \in \mathcal{P}$, find $u_L(\bg{\mu}) \in V_{\texttt{rb}}$ so that
			\label{eq:pde-rb}
			g(u_L(\bg{\mu}), \, v_L; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v_L \in V_{\texttt{rb}} \, .
		Then, Newton's method applied to \eqref{eq:pde-rb} entails, at each iteration $k \geq 0$, the solution of the linearized problem: given $\bg{\mu} \in \mathcal{P}$, seek $\delta u_{L}^k(\bg{\mu})$ such that
			\label{eq:pde-rb-newton}
			dg \big[ u_{L}^k(\bg{\mu}) \big] \big( \delta u_{L}^k(\bg{\mu}), \, v_{L}; \, \bg{\mu} \big) = - g \big( u_{L}^k(\bg{\mu}), \, v_{L}; \, \bg{\mu} \big) \hspace*{0.3cm} \forall v_{L} \in V_{\texttt{rb}} \, ,
		with $u_{L}^{k+1}(\bg{\mu}) = u_{L}^k(\bg{\mu}) + \delta u_{L}^k(\bg{\mu})$. At this stage, it is worth pointing out that the RB functions $\big\lbrace \psi_l \big\rbrace_{1 \leq l \leq L}$ belong to $V_h$, i.e., they are actual FE functions. Hence, denoting by $\bg{\psi}_l \in \mathbb{R}^{N_h}$ the vector collecting the nodal values of $\psi_l$, for $l = 1, \, \ldots \, , L$, let us introduce the matrix \[ \mathbb{V} = \big[ \bg{\psi}_1 \, \big| \, \ldots \, \big| \, \bg{\psi}_L \big] \in \mathbb{R}^{{N_h} \times L} \, .\] For any $v_{L} \in V_{\texttt{rb}}$, the matrix $\mathbb{V}$ encodes the change of variables from the RB basis to the standard (Lagrangian) FE basis, i.e.,
			\label{eq:rb-fe-coefficients}
			\mathbf{v}_L = \mathbb{V} ~ \mathbf{v}_{\texttt{rb}} \, .
		Therefore, each element $v_{L}$ of the reduced space admits two (algebraic) representations:
		\begin{itemize}
			\item $\mathbf{v}_{\texttt{rb}} \in \mathbb{R}^L$, collecting the coefficients for the expansion of $v_{L}$ in terms of the RB basis $\big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace$;
			\item $\mathbf{v}_{L} \in \mathbb{R}^{N_h}$, collecting the coefficients for the expansion of $v_{L}$ in terms of the FE basis $\big\lbrace \phi_1, \, \ldots \, , \phi_{N_h} \big\rbrace$.
		\end{itemize}
		Note that the latter is also available for any $v_h \in V_h$, while the former characterizes the element in the subspace $V_{\texttt{rb}}$. Then, due to \eqref{eq:galerkin-nonlinear-system-equation}, \eqref{eq:rb-fe-coefficients} and the linearity of $g(\cdot,\cdot; \bg{\mu})$ in the second argument, the algebraic formulation of the reduced basis problem \eqref{eq:pde-rb} can be written in compact form as: given $\bg{\mu} \in \mathcal{P}$, seek $\mathbf{u}_{\texttt{rb}} \in \mathbb{R}^L$ such that
			\label{eq:rb-nonlinear-system}
			\mathbf{G}_{\texttt{rb}}(\mathbf{u}_{\texttt{rb}}(\bg{\mu}); \, \bg{\mu}) = \mathbb{V}^T \mathbf{G}_h(\mathbf{u}_L(\bg{\mu}); \, \bg{\mu}) = \mathbb{V}^T \mathbf{G}_h(\mathbb{V} ~ \mathbf{u}_{\texttt{rb}}(\bg{\mu}); \, \bg{\mu}) = \bg{0} ~ \in ~ \mathbb{R}^L \, .
		Observe that this \emph{reduced nonlinear system} imposes the orthogonality (in the Euclidean scalar product) of the residual vector $\mathbf{G}_h(\cdot; \bg{\mu})$, evaluated in $\mathbb{V} \mathbf{u}_{\texttt{rb}}(\bg{\mu})$, to the columns of $\mathbb{V}$, thus encoding the Galerkin approach pursued at the variational level. Finally, exploiting the chain rule and the Jacobian $\mathbb{J}_h(\cdot; \bg{\mu})$ of $\mathbf{G}_h(\cdot; \bg{\mu})$, the Jacobian $\mathbb{J}_{\texttt{rb}}(\cdot; \bg{\mu})$ of $\mathbf{G}_{\texttt{rb}}(\cdot; \bg{\mu})$ is given by
			\label{eq:rb-nonlinear-system-jacobian}
			\mathbb{J}_{\texttt{rb}}(\mathbf{w}; \, \bg{\mu}) = \mathbb{V}^T \mathbb{J}_h(\mathbb{V} ~ \mathbf{w}; \, \bg{\mu}) \, \mathbb{V} ~ \in ~ \mathbb{R}^{L \times L} \hspace*{0.3cm} \forall \mathbf{w} \in \mathbb{R}^L \, , \, \forall \bg{\mu} \in \mathcal{P} \, .
		Hence, starting from an initial guess $\mathbf{u}_{\texttt{rb}}^0 \in \mathbb{R}^L$, each iteration $k$, $k \geq 0$, of Newton's method applied to the reduced nonlinear system \eqref{eq:rb-nonlinear-system} entails the resolution of the linear system
			\label{eq:rb-nonlinear-system-newton}
			\mathbb{J}_{\texttt{rb}}(\mathbf{u}_{\texttt{rb}}^k(\bg{\mu}); \, \bg{\mu}) ~ \delta \mathbf{u}_{\texttt{rb}}^k(\bg{\mu}) = - \mathbf{G}_{\texttt{rb}}(\mathbf{u}_{\texttt{rb}}^k(\bg{\mu}); \, \bg{\mu}) \, ,
		with $\mathbf{u}_{\texttt{rb}}^{k+1}(\bg{\mu}) = \mathbf{u}_{\texttt{rb}}^k(\bg{\mu}) + \delta \mathbf{u}_{\texttt{rb}}^k(\bg{\mu})$. Therefore, applying the POD-Galerkin RB method enables a dramatic reduction of the size of the linear systems to solve whenever the dimension $L$ of the reduced space $V_{\texttt{rb}}$ is much lower than the dimension ${N_h}$ of the underlying finite element space $V_h$.

@@

			V_{\texttt{rb}} = \text{span} \big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace

@@

		\noindent Assume now we seek to approximate the columns of $\mathbb{S}$ by means of $L$ orthonormal vectors $\big\lbrace \wt{\mathbf{w}}_1, \, \ldots \, , \wt{\mathbf{w}}_L \big\rbrace$, with $L < R$. It is an easy matter to show that for each $\mathbf{s}_n$, $n = 1, \, \ldots \, , N$, the element of $\text{span} \big\lbrace \wt{\mathbf{w}}_1, \, \ldots \, , \wt{\mathbf{w}}_L \big\rbrace$ closest to $\mathbf{s}_n$ in the Euclidean norm $\norm{\cdot}_{\mathbb{R}^{N_h}}$ is given by
		\begin{equation*}
			\sum_{l = 1}^L \big( \mathbf{s}_n, \, \wt{\mathbf{w}}_l \big)_{\mathbb{R}^{N_h}} \wt{\mathbf{w}}_l \, .
		\end{equation*} 
		Hence, we could measure the error committed by approximating the columns of $\mathbb{S}$ via the vectors $\big\lbrace \wt{\mathbf{w}}_l \big\rbrace_{1 \leq l \leq L}$ through the quantity
		\begin{equation}
			\label{eq:basis-error}
			\varepsilon(\wt{\mathbf{w}}_1, \, \ldots \, , \wt{\mathbf{w}}_L) = \sum_{n = 1}^N \norm{\mathbf{s}_n - \sum_{l = 1}^L \big( \mathbf{s}_n, \, \wt{\mathbf{w}}_l \big)_{\mathbb{R}^{N_h}} \wt{\mathbf{w}}_l}_{\mathbb{R}^{N_h}}^2 \, .
		\end{equation}
		The Schmidt-Eckart-Young theorem \cite{EY36, Sch07} states that the \emph{POD basis} of rank $L$ $\big\lbrace \mathbf{w}_1, \, \ldots \, , \mathbf{w}_L \big\rbrace$, consisting of the first $L$ left singular values of $\mathbb{S}$, minimizes \eqref{eq:basis-error} among all the orthonormal bases of $\mathbb{R}^L$. Therefore, in the POD-Galerkin RB method, we set $\bg{\psi}_l = \mathbf{w}_l$, for all $l = 1, \, \ldots \, , L$, so that
		\begin{equation*}
			\mathbb{V} = \big[ \mathbf{w}_1 \, \big| \, \ldots \, \big| \, \mathbf{w}_L \big] \, . %\, \footnote{Please observe that generally we do not decorate $\mathbb{V}$ with any subscript nor superscript reporting the dimension of the reduced basis it represents, unless not clear from the context.} \, .
		\end{equation*}
		%Hence, in the reduced basis problem \eqref{eq:pde-rb} the test and trial functions are picked from the subspace $V_{\texttt{rb}}$ of $V_h$ spanned by the functions $\big\lbrace \psi_l \big\rbrace_{1 \leq l \leq L}$, given by
		%\begin{equation}
		%	\label{eq:pod-fe-basis-functions}
		%	\psi_l(\bg{x}) = \sum_{m = 1}^{N_h} \psi_l^{(m)} ~ \phi_m(\bg{x}) = \sum_{m = 1}^{N_h} (\mathbf{w}_l)_m ~ \phi_m(\bg{x}) \hspace*{0.3cm} \text{for $1 \leq l \leq L$} \, .
		%\end{equation}

@@

		\begin{algorithm}[t]	
			\begin{algorithmic}[1]
				\Function{$\mathbb{V} = $ \textsc{PODG\_offline}}{$\mathcal{P}$, $\Omega_h$, $N$}
					\State generate the parameter set $\Xi_N = \big\lbrace \bg{\mu}^{(1)}, \, \ldots \, , \bg{\mu}^{(N)} \big\rbrace$
					\State compute the high-fidelity solutions $\big\lbrace \mathbf{u}_h \big( \bg{\mu}^{(1)} \big), \, \ldots \, , \mathbf{u}_h \big( \bg{\mu}^{(N)} \big) \big\rbrace$ via FE-Newton's method
					\State generate the POD basis functions $\big\lbrace \mathbf{w}_1, \, \ldots \, , \mathbf{w}_L \big\rbrace$ via method of snapshots
					\State assemble $\mathbb{V} = \big[ \mathbf{w}_1 \, \big| \, \ldots \, \big| \, \mathbf{w}_L \big]$
				\EndFunction

@@

		\begin{figure}[t]
			\center
			\includegraphics[scale = 0.55]{neural_model_ter.eps}

>>>>

@@

		Let $V_h \subset V$ be a suitable FE subspace of $V$ of (finite) dimension $N_h$, with $h \geq 0$ being the characteristic size of the underlying mesh $\Omega_h$ which discretizes $\Omega$. The FE approximation of the weak problem \eqref{eq:pde-weak-reference} can be cast in the form: given $\bg{\mu} \in \mathcal{P}$, find $u_h(\bg{\mu}) \in V_h$ such that 
		\begin{equation}
			\label{eq:galerkin}
			g(u_h(\bg{\mu}), \, v_h; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v_h \in V_h \, .
		\end{equation}
		%The discretization \eqref{eq:galerkin} is known as \emph{Galerkin approximation}, and therefore $u_h(\bg{\mu})$ is referred to as the \emph{Galerkin solution} to the problem \eqref{eq:pde-differential-reference}. 
		Due to the nonlinearity of $g(\cdot, \, \cdot; \, \bg{\mu})$ in its first argument, one has to resort to some iterative method, e.g., Newton's method, to solve the Galerkin problem \eqref{eq:galerkin}. In this regard, let \[ dg[z](\cdot, \, \cdot; \, \bg{\mu}) ~ : ~ V \times V \rightarrow \mathbb{R} \]
		be the partial Frech\'et derivative of $g(\cdot, \, \cdot; \, \bg{\mu})$ with respect to its first argument, evaluated at $z \in V$. Starting from an initial guess $u_h^0(\bg{\mu})$, we construct a collection of approximations $\big\lbrace u_h^k(\bg{\mu}) \big\rbrace_{k \geq 0}$ to the Galerkin solution $u_h(\bg{\mu})$ by iteratively solving the linearized problems
		\begin{equation*}
			\label{eq:newton-linearized-problem}
			dg \big[ u_h^k(\bg{\mu}) \big](\delta u_h^k(\bg{\mu}), \, v_h; \, \bg{\mu}) = - g(u_h^k(\bg{\mu}), \, v_h; \, \bg{\mu}) \hspace*{0.3cm} \forall v_h \in V_h
		\end{equation*}
		in the unknown $\delta u_h^k(\bg{\mu}) \in V_h$, and then setting $u_h^{k+1}(\bg{\mu}) = u_h^k(\bg{\mu}) + \delta u_h^k(\bg{\mu})$.

@@

		As detailed in the previous subsection, the finite element discretization of the $\bg{\mu}$-dependent nonlinear differential problem \eqref{eq:pde-weak-reference}, combined with Newton's method, entails the assembly and resolution of (possibly) many linear systems of the form \eqref{eq:galerkin-linear-system}, whose dimension $N_h$ is directly related to $(i)$ the size of the underlying grid and $(ii)$ the order of the polynomial FE space adopted. Since the accuracy of the resulting discretization heavily relies on these two factors, a direct numerical approximation of the full-order model implies severe computational costs. Therefore, this approach is hardly affordable in \emph{many-query} and \emph{real-time} contexts, even resorting to high-performance parallel workstations. %where one is interested in a fast and reliable prediction of an \emph{output of interest}, i.e, a functional of the field variable $u(\bg{\mu})$, for many instances of $\bg{\mu} \in \mathcal{P}$ \cite{Dep08}. 
		This motivates the broad use of \emph{reduced-order} models across several inter-disciplinary areas \cite{HSR16, QMN15}. %, e.g., parameter estimation, optimal control, shape optimization and uncertainty quantification \cite{HSR16, QMN15}.

		Reduced basis methods seek an approximated solution to problem \eqref{eq:pde-weak-reference} as a linear combination of parameter-independent functions $\big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace \subset V_h$, called \emph{reduced basis functions}, built from a collection of high-fidelity snapshots $\big\lbrace u_h \left( \bg{\mu}^{(1)} \right), \, \ldots \, , u_h \left( \bg{\mu}^{(N)} \right) \big\rbrace$, where the discrete and finite set $\Xi_N = \big\lbrace \bg{\mu}^{(1)}, \, \ldots \, , \bg{\mu}^{(N)} \big\rbrace \subset \mathcal{P}$ may consist of either a uniform lattice or randomly generated points over the parameter domain $\mathcal{P}$ \cite{HSR16}. The basis functions \smash{$\big\lbrace \psi_l \big\rbrace_{1 \leq l \leq L}$} generally follow from a principal component analysis (PCA) of the set of snapshots (in that case, $N > L$), or they might coincide with the snapshots themselves (in that case, $N = L$). In the latter approach, typical of any \emph{greedy} method, the parameters \smash{$\big\lbrace \bg{\mu}^{(n)} \big\rbrace_{1 \leq n \leq N}$} must be carefully chosen according to some optimality criterium (see, e.g., \cite{Chen17}). Here, we pursue the first approach, employing the well-known proper orthogonal decomposition (POD) method \cite{Lia02, Vol08}, detailed in the following subsection. For now, assume that a reduced basis is available and let $V_{\texttt{rb}} \subset V_h$ be the associated \emph{reduced basis space}, i.e.,
		\begin{equation*}
			V_{\texttt{rb}} = \text{span} \big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace \, .
		\end{equation*} 
		A \emph{reduced basis solution} $u_{L}(\bg{\mu})$ is sought in the form
		\begin{equation*}
			\label{eq:rb-solution}
			u_{L}(\bg{x}; \, \bg{\mu}) = \sum_{l = 1}^L u_{\texttt{rb}}^{(l)}(\bg{\mu}) ~ \psi_l(\bg{x}) ~ \in ~ V_{\texttt{rb}} \, ,
		\end{equation*}
		with \[ \mathbf{u}_{\texttt{rb}}(\bg{\mu}) = \big[ u_{\texttt{rb}}^{(1)}(\bg{\mu}), \, \ldots \, , u_{\texttt{rb}}^{(L)}(\bg{\mu}) \big]^T \in \mathbb{R}^L \] be the \emph{reduced coefficients} (also called \emph{generalized coordinates}) for the expansion of the RB solution in the RB basis functions. To unearth $u_L(\bg{\mu})$, we proceed to project the variational problem \eqref{eq:pde-weak-reference} onto the RB space $V_{\texttt{rb}}$ by pursuing a standard Galerkin approach, leading to the following \emph{reduced basis problem}: given $\bg{\mu} \in \mathcal{P}$, find $u_L(\bg{\mu}) \in V_{\texttt{rb}}$ so that
		\begin{equation}
			\label{eq:pde-rb}
			g(u_L(\bg{\mu}), \, v_L; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v_L \in V_{\texttt{rb}} \, .
		\end{equation}
		Then, Newton's method applied to \eqref{eq:pde-rb} entails, at each iteration $k \geq 0$, the solution of the linearized problem: given $\bg{\mu} \in \mathcal{P}$, seek $\delta u_{L}^k(\bg{\mu})$ such that
		\begin{equation*}
			\label{eq:pde-rb-newton}
			dg \big[ u_{L}^k(\bg{\mu}) \big] \big( \delta u_{L}^k(\bg{\mu}), \, v_{L}; \, \bg{\mu} \big) = - g \big( u_{L}^k(\bg{\mu}), \, v_{L}; \, \bg{\mu} \big) \hspace*{0.3cm} \forall v_{L} \in V_{\texttt{rb}} \, ,
		\end{equation*}
		with $u_{L}^{k+1}(\bg{\mu}) = u_{L}^k(\bg{\mu}) + \delta u_{L}^k(\bg{\mu})$.

		At this stage, it is worth pointing out that the RB functions $\big\lbrace \psi_l \big\rbrace_{1 \leq l \leq L}$ belong to $V_h$, i.e., they are actual FE functions. Hence, denoting by $\bg{\psi}_l \in \mathbb{R}^{N_h}$ the vector collecting the nodal values of $\psi_l$, for $l = 1, \, \ldots \, , L$, let us introduce the matrix \[ \mathbb{V} = \big[ \bg{\psi}_1 \, \big| \, \ldots \, \big| \, \bg{\psi}_L \big] \in \mathbb{R}^{{N_h} \times L} \, .\] For any $v_{L} \in V_{\texttt{rb}}$, the matrix $\mathbb{V}$ encodes the change of variables from the RB basis to the standard (Lagrangian) FE basis, i.e.,
		\begin{equation}
			\label{eq:rb-fe-coefficients}
			\mathbf{v}_L = \mathbb{V} ~ \mathbf{v}_{\texttt{rb}} \, .
		\end{equation}
		%Therefore, each element $v_{L}$ of the reduced space admits two (algebraic) representations:
		%\begin{itemize}
		%	\item $\mathbf{v}_{\texttt{rb}} \in \mathbb{R}^L$, collecting the coefficients for the expansion of $v_{L}$ in terms of the RB basis $\big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace$;
		%	\item $\mathbf{v}_{L} \in \mathbb{R}^{N_h}$, collecting the coefficients for the expansion of $v_{L}$ in terms of the FE basis $\big\lbrace \phi_1, \, \ldots \, , \phi_{N_h} \big\rbrace$.
		%\end{itemize}
		%Note that the latter is also available for any $v_h \in V_h$, while the former characterizes the element in the subspace $V_{\texttt{rb}}$. 
		Then, due to \eqref{eq:galerkin-nonlinear-system-equation}, \eqref{eq:rb-fe-coefficients} and the linearity of $g(\cdot,\cdot; \bg{\mu})$ in the second argument, the algebraic formulation of the reduced basis problem \eqref{eq:pde-rb} can be written in compact form as: given $\bg{\mu} \in \mathcal{P}$, seek $\mathbf{u}_{\texttt{rb}} \in \mathbb{R}^L$ such that
		\begin{equation}
			\label{eq:rb-nonlinear-system}
			\mathbf{G}_{\texttt{rb}}(\mathbf{u}_{\texttt{rb}}(\bg{\mu}); \, \bg{\mu}) = \mathbb{V}^T \mathbf{G}_h(\mathbf{u}_L(\bg{\mu}); \, \bg{\mu}) = \mathbb{V}^T \mathbf{G}_h(\mathbb{V} ~ \mathbf{u}_{\texttt{rb}}(\bg{\mu}); \, \bg{\mu}) = \bg{0} ~ \in ~ \mathbb{R}^L \, .
		\end{equation}
		Observe that this \emph{reduced nonlinear system} imposes the orthogonality (in the Euclidean scalar product) of the residual vector $\mathbf{G}_h(\cdot; \bg{\mu})$, evaluated in $\mathbb{V} ~ \mathbf{u}_{\texttt{rb}}(\bg{\mu})$, to the columns of $\mathbb{V}$, thus encoding the Galerkin approach pursued at the variational level. Finally, exploiting the chain rule and the Jacobian $\mathbb{J}_h(\cdot; \bg{\mu})$ of $\mathbf{G}_h(\cdot; \bg{\mu})$, the Jacobian $\mathbb{J}_{\texttt{rb}}(\cdot; \bg{\mu})$ of $\mathbf{G}_{\texttt{rb}}(\cdot; \bg{\mu})$ is given by
		\begin{equation}
			\label{eq:rb-nonlinear-system-jacobian}
			\mathbb{J}_{\texttt{rb}}(\mathbf{w}; \, \bg{\mu}) = \mathbb{V}^T \mathbb{J}_h(\mathbb{V} ~ \mathbf{w}; \, \bg{\mu}) \, \mathbb{V} ~ \in ~ \mathbb{R}^{L \times L} \hspace*{0.3cm} \forall \mathbf{w} \in \mathbb{R}^L \, , \, \forall \bg{\mu} \in \mathcal{P} \, .
		\end{equation}
		Hence, starting from an initial guess $\mathbf{u}_{\texttt{rb}}^0 \in \mathbb{R}^L$, each iteration $k$, $k \geq 0$, of Newton's method applied to the reduced nonlinear system \eqref{eq:rb-nonlinear-system} entails the resolution of the linear system
		\begin{equation}
			\label{eq:rb-nonlinear-system-newton}
			\mathbb{J}_{\texttt{rb}}(\mathbf{u}_{\texttt{rb}}^k(\bg{\mu}); \, \bg{\mu}) ~ \delta \mathbf{u}_{\texttt{rb}}^k(\bg{\mu}) = - \mathbf{G}_{\texttt{rb}}(\mathbf{u}_{\texttt{rb}}^k(\bg{\mu}); \, \bg{\mu}) \, ,
		\end{equation}
		with $\mathbf{u}_{\texttt{rb}}^{k+1}(\bg{\mu}) = \mathbf{u}_{\texttt{rb}}^k(\bg{\mu}) + \delta \mathbf{u}_{\texttt{rb}}^k(\bg{\mu})$. Therefore, applying the POD-Galerkin RB method enables a dramatic reduction of the size of the linear systems to solve whenever the dimension $L$ of the reduced space $V_{\texttt{rb}}$ is much lower than the dimension ${N_h}$ of the underlying finite element space $V_h$.

@@

		%\begin{equation*}
		%	V_{\texttt{rb}} = \text{span} \big\lbrace \psi_1, \, \ldots \, , \psi_L \big\rbrace
		%\end{equation*}

@@

		\noindent At the algebraic level, our goal is to approximate the columns of $\mathbb{S}$ by means of $L$ orthonormal vectors $\big\lbrace \wt{\mathbf{w}}_1, \, \ldots \, , \wt{\mathbf{w}}_L \big\rbrace$, with $L < R$. It is an easy matter to show that for each $\mathbf{s}_n$, $n = 1, \, \ldots \, , N$, the element of $\text{span} \big\lbrace \wt{\mathbf{w}}_1, \, \ldots \, , \wt{\mathbf{w}}_L \big\rbrace$ closest to $\mathbf{s}_n$ in the Euclidean norm $\norm{\cdot}_{\mathbb{R}^{N_h}} = \sqrt{(\cdot,\cdot)_{\mathbb{R}^{N_h}}}$ is given by
		\begin{equation*}
			\sum_{l = 1}^L \big( \mathbf{s}_n, \, \wt{\mathbf{w}}_l \big)_{\mathbb{R}^{N_h}} \wt{\mathbf{w}}_l \, .
		\end{equation*} 
		Hence, we could measure the error committed by approximating the columns of $\mathbb{S}$ via the vectors $\big\lbrace \wt{\mathbf{w}}_l \big\rbrace_{1 \leq l \leq L}$ through the quantity
		\begin{equation}
			\label{eq:basis-error}
			\varepsilon(\wt{\mathbf{w}}_1, \, \ldots \, , \wt{\mathbf{w}}_L) = \sum_{n = 1}^N \norm{\mathbf{s}_n - \sum_{l = 1}^L \big( \mathbf{s}_n, \, \wt{\mathbf{w}}_l \big)_{\mathbb{R}^{N_h}} \wt{\mathbf{w}}_l}_{\mathbb{R}^{N_h}}^2 \, .
		\end{equation}
		The Schmidt-Eckart-Young theorem \cite{EY36, Sch07} states that the \emph{POD basis} of rank $L$ $\big\lbrace \mathbf{w}_1, \, \ldots \, , \mathbf{w}_L \big\rbrace$, consisting of the first $L$ left singular values of $\mathbb{S}$, minimizes \eqref{eq:basis-error} among all the orthonormal bases of $\mathbb{R}^L$. Therefore, in the POD-Galerkin RB method, we set $\bg{\psi}_l = \mathbf{w}_l$, for all $l = 1, \, \ldots \, , L$, so that
		\begin{equation*}
			\mathbb{V} = \big[ \mathbf{w}_1 \, \big| \, \ldots \, \big| \, \mathbf{w}_L \big] \, . %\, \footnote{Please observe that generally we do not decorate $\mathbb{V}$ with any subscript nor superscript reporting the dimension of the reduced basis it represents, unless not clear from the context.} \, .
		\end{equation*}
		%Hence, in the reduced basis problem \eqref{eq:pde-rb} the test and trial functions are picked from the subspace $V_{\texttt{rb}}$ of $V_h$ spanned by the functions $\big\lbrace \psi_l \big\rbrace_{1 \leq l \leq L}$, given by
		%\begin{equation}
		%	\label{eq:pod-fe-basis-functions}
		%	\psi_l(\bg{x}) = \sum_{m = 1}^{N_h} \psi_l^{(m)} ~ \phi_m(\bg{x}) = \sum_{m = 1}^{N_h} (\mathbf{w}_l)_m ~ \phi_m(\bg{x}) \hspace*{0.3cm} \text{for $1 \leq l \leq L$} \, .
		%\end{equation}

@@

		\begin{algorithm}[b!]	
			\begin{algorithmic}[1]
				\Function{$\mathbb{V} = $ \textsc{PODG\_offline}}{$\mathcal{P}$, $\Omega_h$, $N$}
					\State generate the parameter set $\Xi_N = \big\lbrace \bg{\mu}^{(1)}, \, \ldots \, , \bg{\mu}^{(N)} \big\rbrace$
					\State compute the high-fidelity solutions $\big\lbrace \mathbf{u}_h \big( \bg{\mu}^{(1)} \big), \, \ldots \, , \mathbf{u}_h \big( \bg{\mu}^{(N)} \big) \big\rbrace$ via FE-Newton's method
					\State generate the POD basis functions $\big\lbrace \mathbf{w}_1, \, \ldots \, , \mathbf{w}_L \big\rbrace$ via method of snapshots
					\State assemble $\mathbb{V} = \big[ \mathbf{w}_1 \, \big| \, \ldots \, \big| \, \mathbf{w}_L \big]$
				\EndFunction

@@

		\begin{figure}[t]
			\begin{minipage}{0.49\textwidth}
				\center
				\vspace*{-0.35cm}
				\includegraphics[scale = 0.55]{neural_model_ter.eps}
			\end{minipage}
			\begin{minipage}{0.49\textwidth}
				\center
				\includegraphics[scale = 0.55]{neural_model_bias.eps}
			\end{minipage}
